The title

### 2024-08-27 05_Manuscript/manuscript.Rmd
a bit of updates

apply(sona %>% 
          select(Q2_1:Q2_21, Q4_1:Q4_20, Q5_1:Q5_20), 
      2, mean, na.rm = TRUE)
apply(sona %>% 
          select(Q2_1:Q2_21, Q4_1:Q4_20, Q5_1:Q5_20), 
      2, sd, na.rm = TRUE)
# check reverse items? Q2_21?

@@

```{r screen-sona-SAD}
# SAD 
nomissing <- import("../03_Data/sona_data_replaced.csv")

@@

# Total
nomissing$totalbad <- page1$badTotal + page2$badTotal + page3$badTotal

nomissing$totalbadUP = 
  page1$badChar + page1$badClick + page1$badMC + 
  page2$badChar + page2$badClick + page2$badMC + 
  page3$badChar + page3$badClick + page3$badMC
table(nomissing$totalbadUP)
nolowqual = subset(nomissing, totalbadUP < 4)
##B&S say 2/5 which is 40%, so 40% of the 9 total is 3.6 or 4 or more

@@

# > nrow(master)
# [1] 564
# > nrow(nomissing)
# [1] 557
# > nrow(nolowqual)
# [1] 507
# > nrow(noout)
# [1] 464

sona_screen_1 <- SAD(
  dat = sona %>% 
    select(Q2_1:Q2_21, `Q10_Page Submit`, `Q10_Click Count`),
  rt = "Q10_Page Submit",
  min = 1,
  max = 5, 
  partno = "ResponseId",
  clicks = "Q10_Click Count",

)

## args: dat: Dataframe of scale values, with each row being a participant and each column being a scale question
## args: rt: vector of response time/page time for each participant
## args: min: minimum value of scale
## args: max: maximum value of scale
## args: partno: vector of corresponding participant numbers
## args: clicks: click count column, outputted by qualtrics
## args: manvec: vector of manipulation check question responses
## args: mancor: correct answer of manipulation check
## args: char: number of characters on the page
```

>>>>

apply(sona %>% 
          select(Q2_1:Q2_21, Q4_1:Q4_20, Q5_1:Q5_20), 
      2, mean, na.rm = TRUE)
apply(sona %>% 
          select(Q2_1:Q2_21, Q4_1:Q4_20, Q5_1:Q5_20), 
      2, sd, na.rm = TRUE)
#

@@

```{r screen-sona-SAD, eval = F}
# SAD 
nomissing <- import("../03_Data/sona_data_replaced.csv")

@@

# Total
nomissing$totalbad <- page1$badTotal + page2$badTotal + page3$badTotal
table(nomissing$totalbad) 
sum(nomissing$totalbad < 15*.4) 
nrow(nomissing)

nomissing$totalbadUP <- 
  page1$badChar + page1$badClick + page1$badMC + 
  page2$badChar + page2$badClick + page2$badMC + 
  page3$badChar + page3$badClick + page3$badMC
table(nomissing$totalbadUP)
sum(nomissing$totalbadUP < 9*.4) 
# B&S say 2/5 which is 40%, so 40% of the 9 total is 3.6 or 4 or more

nolowqual <- subset(nomissing, totalbadUP < 4)
write.csv(nolowqual, "../03_Data/sona_data_goodqual.csv", row.names = F)
```

```{r}

@@

```
